A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-13 paper/main.tex
paper: improve placing of ks31

\piccaption{Conway's 31 vector Kochen-Specker system\label{fig:conway31}}
\parpic[r]{%
%  Based on  <http://www.latex-community.org/viewtopic.php?f=4&t=2111>
\begin{tikzpicture}[scale=0.8,
        style={inner sep=0pt,%
              outer sep=2pt,%
              mark coordinate/.style={%
                inner sep=0pt,outer sep=0pt,minimum size=4pt,
                fill=black,circle}%
            }]
\def\R{2.5} % sphere radius
\def\St{1.41421356237}
\def\ST{1.73205080757}
\filldraw[ball color=white] (0,0) circle (\R);
\coordinate[mark coordinate] (N) at (0,0);
\coordinate[mark coordinate] (N) at (0,-\R/\St);
\coordinate[mark coordinate] (N) at (0,-\R*\St);
\coordinate[mark coordinate] (N) at (0,\R*\St/4);
\coordinate[mark coordinate] (N) at (0,\R*\St/2);
\coordinate[mark coordinate] (N) at (0,3*\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/8,3*\R*\St/8);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/8,5*\R*\St/8);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,0);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-\R*\St/2);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-3*\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,\R*\St/2);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,\R*\St/8);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,-\R*\St/8);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,-3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,5*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-5*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,0);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,\R*\St/2);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-\R*\St/2);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-3*\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,-\R/\St);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,0);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,\R/\St);
\draw (0,0) -- (0,-\R*\St) -- (-\R*\St*\ST/2,-\R/\St) --  (-\R*\St*\ST/2,\R/\St)
    --  (0,\R*\St) -- (\R*\St*\ST/2,\R/\St) 
    -- (\R*\St*\ST/2,-\R/\St) -- (0,- \R*\St);
\draw  (-\R*\St*\ST/2,\R/\St) -- (0,0) -- (\R*\St*\ST/2,\R/\St);
\draw (-\R*\St*\ST/4, -3*\R*\St/4) -- (-\R*\St*\ST/4,\R*\St/4 )
    -- (\R*\St*\ST/4, 3*\R*\St/4) ;
\draw (\R*\St*\ST/4, -3*\R*\St/4) -- (\R*\St*\ST/4,\R*\St/4 )
    -- (-\R*\St*\ST/4, 3*\R*\St/4) ;
\draw  (-\R*\St*\ST/2,{\R/\St - \R*\St/4}) -- (0,- \R*\St/4)
    -- (\R*\St*\ST/2,{\R/\St - \R*\St/4});
\draw  (-\R*\St*\ST/2,{\R/\St - \R*\St/2}) -- (0,- \R*\St/2)
    -- (\R*\St*\ST/2,{\R/\St - \R*\St/2});
\draw  (-\R*\St*\ST/2,{\R/\St - 3*\R*\St/4}) -- (0,- 3*\R*\St/4)
    -- (\R*\St*\ST/2,{\R/\St - 3*\R*\St/4});
\draw(-\R*\St*\ST/8,-0.25*7*\R/\St) -- (-\R*\St*\ST/8,{-0.25*7*\R/\St + \R*\St})
    -- (3*\R*\St*\ST/8,5*0.25*\R/\St);
\draw(\R*\St*\ST/8,-0.25*7*\R/\St) -- (\R*\St*\ST/8,{-0.25*7*\R/\St + \R*\St})
    -- (-3*\R*\St*\ST/8,5*0.25*\R/\St);
\draw (-3*\R*\St*\ST/8,-5*0.25*\R/\St)
    -- (-3*\R*\St*\ST/8,{-5*0.25*\R/\St + \R*\St})
    -- (\R*\St*\ST/8,0.25*7*\R/\St);
\draw (3*\R*\St*\ST/8,-5*0.25*\R/\St)
    -- (3*\R*\St*\ST/8,{-5*0.25*\R/\St + \R*\St})
    -- (-\R*\St*\ST/8,0.25*7*\R/\St);
\undef\R
\undef\ST
\undef\St
\end{tikzpicture}}

>>>>

\piccaption{Conway's 31 vector Kochen-Specker system\label{fig:conway31}}
\parpic[r]{%
%  Based on  <http://www.latex-community.org/viewtopic.php?f=4&t=2111>
\begin{tikzpicture}[scale=0.75,
        style={inner sep=0pt,%
              outer sep=2pt,%
              mark coordinate/.style={%
                inner sep=0pt,outer sep=0pt,minimum size=4pt,
                fill=black,circle}%
            }]
\def\R{2.5} % sphere radius
\def\St{1.41421356237}
\def\ST{1.73205080757}
\filldraw[ball color=white] (0,0) circle (\R);
\coordinate[mark coordinate] (N) at (0,0);
\coordinate[mark coordinate] (N) at (0,-\R/\St);
\coordinate[mark coordinate] (N) at (0,-\R*\St);
\coordinate[mark coordinate] (N) at (0,\R*\St/4);
\coordinate[mark coordinate] (N) at (0,\R*\St/2);
\coordinate[mark coordinate] (N) at (0,3*\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/8,3*\R*\St/8);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/8,5*\R*\St/8);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,0);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-\R*\St/2);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,-3*\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,\R*\St/4);
\coordinate[mark coordinate] (N) at (-\R*\St*\ST/4,\R*\St/2);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,\R*\St/8);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,-\R*\St/8);
\coordinate[mark coordinate] (N) at (-3*\R*\St*\ST/8,-3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,5*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-3*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/8,-5*\R*\St/8);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,0);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,\R*\St/2);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-\R*\St/2);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/4,-3*\R*\St/4);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,-\R/\St);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,0);
\coordinate[mark coordinate] (N) at (\R*\St*\ST/2,\R/\St);
\draw (0,0) -- (0,-\R*\St) -- (-\R*\St*\ST/2,-\R/\St) --  (-\R*\St*\ST/2,\R/\St)
    --  (0,\R*\St) -- (\R*\St*\ST/2,\R/\St) 
    -- (\R*\St*\ST/2,-\R/\St) -- (0,- \R*\St);
\draw  (-\R*\St*\ST/2,\R/\St) -- (0,0) -- (\R*\St*\ST/2,\R/\St);
\draw (-\R*\St*\ST/4, -3*\R*\St/4) -- (-\R*\St*\ST/4,\R*\St/4 )
    -- (\R*\St*\ST/4, 3*\R*\St/4) ;
\draw (\R*\St*\ST/4, -3*\R*\St/4) -- (\R*\St*\ST/4,\R*\St/4 )
    -- (-\R*\St*\ST/4, 3*\R*\St/4) ;
\draw  (-\R*\St*\ST/2,{\R/\St - \R*\St/4}) -- (0,- \R*\St/4)
    -- (\R*\St*\ST/2,{\R/\St - \R*\St/4});
\draw  (-\R*\St*\ST/2,{\R/\St - \R*\St/2}) -- (0,- \R*\St/2)
    -- (\R*\St*\ST/2,{\R/\St - \R*\St/2});
\draw  (-\R*\St*\ST/2,{\R/\St - 3*\R*\St/4}) -- (0,- 3*\R*\St/4)
    -- (\R*\St*\ST/2,{\R/\St - 3*\R*\St/4});
\draw(-\R*\St*\ST/8,-0.25*7*\R/\St) -- (-\R*\St*\ST/8,{-0.25*7*\R/\St + \R*\St})
    -- (3*\R*\St*\ST/8,5*0.25*\R/\St);
\draw(\R*\St*\ST/8,-0.25*7*\R/\St) -- (\R*\St*\ST/8,{-0.25*7*\R/\St + \R*\St})
    -- (-3*\R*\St*\ST/8,5*0.25*\R/\St);
\draw (-3*\R*\St*\ST/8,-5*0.25*\R/\St)
    -- (-3*\R*\St*\ST/8,{-5*0.25*\R/\St + \R*\St})
    -- (\R*\St*\ST/8,0.25*7*\R/\St);
\draw (3*\R*\St*\ST/8,-5*0.25*\R/\St)
    -- (3*\R*\St*\ST/8,{-5*0.25*\R/\St + \R*\St})
    -- (-\R*\St*\ST/8,0.25*7*\R/\St);
\undef\R
\undef\ST
\undef\St
\end{tikzpicture}}
